Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-05-01 icdm/submission/includes/results.tex
splitted results into evalutation and results
updated adadelta table

\section{Results}\label{chap:results}

@@

\subsection{Results by optimizer}
We ran multiple experiments for each optimizer. This subsection will only give an overview of the achieved results. Each subsection will give an explanation over the achieved result with a specific optimizer.

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.45]{images/results_sgd_shuffle}
\caption{Training time Stochastic Gradient Descent with input Shuffling}
\label{fig:results_sgd}
\end{figure}
\subsubsection{Momentum and Nesterov}
Momentum and NAG \cite{nag} both have an additional hyperparameter $\gamma$, that, as described in Section \ref{optimizers}, defines the percentage of the previous gradient that will be added to the current gradients. We set $\gamma = 0.9$ as this is the typical value and did not alter it during our experiments. Momentum and Nesterov alone respectively only slightly decrease or increase the convergence time. Momentum optimally converges in 9 epochs and Nesterov in 13. If we combine these optimizers with input shuffling, interestingly the same phenomena as with plain SGD appear. The convergence time gets better, 8 epochs for Momentum and 3 epochs for NAG. The phenomena that a higher learning rat yields better results also happens with both of the optimizers. As Momentum does not converge in 20 epochs with a learning rate of 0.002 but does in 8 with input shuffling.
\begin{figure}[h]
\centering
\begin{minipage}{.5\textwidth}
\centering
\includegraphics[scale=0.3]{images/results_mom_shuffle}
\caption{Training time Momentum with input Shuffling}
\label{fig:results_mom}
\label{fig:test1}
\end{minipage}%
\begin{minipage}{.5\textwidth}
\centering
\includegraphics[scale=0.3]{images/results_nag_shuffle}
\caption{Training time Nesterov with input Shuffling}
\label{fig:results_nag}
\end{minipage}
\end{figure}
\subsubsection{Adagrad}
Adagrad \cite{adagrad} is a very interesting tool for learning word embeddings as it decreases the learning rate for very frequent occurring features, and vice versa (this is explained in detail in Section \ref{ssec:adagrad}). Because words that appear very frequently often do not have a semantic gain that is as important as words that appear less frequently to their context words, it's good to have a lower learning rate. So, in theory, Adagrad is particularly well suited for our task. This was confirmed empirically as our model converged in 4 epochs. When combined with shuffling Adagrad only took 3 epochs to converge. This shows the tendency of the skip gram model to converge faster with input shuffling and the big impact of having different learning rate for each feature.
Here it's interesting to notice that a higher learning rate combined with input shuffling did not yield better results than without shuffling. Both of our best results happened with a learning rate of $0.1$, as shown in Figure \ref{fig:results_adagrad_shuffle}.
\begin{figure}[h]
\centering
\includegraphics[scale=0.45]{images/results_adagrad_shuffle}
\caption{Training time Adagrad with input Shuffling}
\label{fig:results_adagrad_shuffle}
\end{figure}
\subsubsection{Adadelta}
In theory Adadelta \cite{adadelta} should outperform Adagrad as it's an extension of the former. Because it didn't have any learning rate to tune, we only did 2 experiments, with and without input shuffling. We are aware of the fact that there are additional hyperparameters but did, for simplicity reason, and because their effect is not as high as the learning rate in other optimizers, decide not to tune it. We left it to its default value $\rho = 0.9$. This parameter defines the percentage taken when calculating the exponentially decaying average of past gradients, as explained in \ref{ssec:adadelta} Adadelta did not manage to achieve a word similarity of 0.66. It only converged to a similarity of 0.59. It did this in 20 epochs without input shuffling and in 3 with input shuffling, as can be seen in Table \ref{table:results_adadelta}
\begin{table}[h]
\centering
\begin{tabular}{|l|l|l|}
\hline
Adadelta Model & Convergence Time & Word similarity \\ \hline
Without Shuffling & 20 & 0.59 \\ \hline
With Shuffling & 3 & 0.59 \\ \hline
\end{tabular}
\caption{Convergence Time and Quality with Adadelta}
\label{table:results_adadelta}
\end{table}

>>>>

\section{Evalutation}\label{chap:results}

@@

\subsection{Results}
We ran multiple experiments for each optimizer. This subsection will only give an overview of the achieved results. Each subsection will give an explanation over the achieved result with a specific optimizer.

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.45]{images/results_sgd_shuffle}
\caption{Training time Stochastic Gradient Descent with input Shuffling}
\label{fig:results_sgd}
\end{figure}
\subsubsection{Momentum and Nesterov}
Momentum and NAG \cite{nag} both have an additional hyperparameter $\gamma$, that, as described in Section \ref{optimizers}, defines the percentage of the previous gradient that will be added to the current gradients. We set $\gamma = 0.9$ as this is the typical value and did not alter it during our experiments. Momentum and Nesterov alone respectively only slightly decrease or increase the convergence time. Momentum optimally converges in 9 epochs and Nesterov in 13. If we combine these optimizers with input shuffling, interestingly the same phenomena as with plain SGD appear. The convergence time gets better, 8 epochs for Momentum and 3 epochs for NAG. The phenomena that a higher learning rat yields better results also happens with both of the optimizers. As Momentum does not converge in 20 epochs with a learning rate of 0.002 but does in 8 with input shuffling.
\begin{figure}[h]
\centering
\begin{minipage}{.5\textwidth}
\centering
\includegraphics[scale=0.3]{images/results_mom_shuffle}
\caption{Training time Momentum with input Shuffling}
\label{fig:results_mom}
\label{fig:test1}
\end{minipage}%
\begin{minipage}{.5\textwidth}
\centering
\includegraphics[scale=0.3]{images/results_nag_shuffle}
\caption{Training time Nesterov with input Shuffling}
\label{fig:results_nag}
\end{minipage}
\end{figure}
\subsubsection{Adagrad}
Adagrad \cite{adagrad} is a very interesting tool for learning word embeddings as it decreases the learning rate for very frequent occurring features, and vice versa (this is explained in detail in Section \ref{ssec:adagrad}). Because words that appear very frequently often do not have a semantic gain that is as important as words that appear less frequently to their context words, it's good to have a lower learning rate. So, in theory, Adagrad is particularly well suited for our task. This was confirmed empirically as our model converged in 4 epochs. When combined with shuffling Adagrad only took 3 epochs to converge. This shows the tendency of the skip gram model to converge faster with input shuffling and the big impact of having different learning rate for each feature.
Here it's interesting to notice that a higher learning rate combined with input shuffling did not yield better results than without shuffling. Both of our best results happened with a learning rate of $0.1$, as shown in Figure \ref{fig:results_adagrad_shuffle}.
\begin{figure}[h]
\centering
\includegraphics[scale=0.45]{images/results_adagrad_shuffle}
\caption{Training time Adagrad with input Shuffling}
\label{fig:results_adagrad_shuffle}
\end{figure}
\subsubsection{Adadelta}
In theory Adadelta \cite{adadelta} should outperform Adagrad as it's an extension of the former. Because it didn't have any learning rate to tune, we only did 2 experiments, with and without input shuffling. We are aware of the fact that there are additional hyperparameters but did, for simplicity reason, and because their effect is not as high as the learning rate in other optimizers, decide not to tune it. We left it to its default value $\rho = 0.9$. This parameter defines the percentage taken when calculating the exponentially decaying average of past gradients, as explained in \ref{ssec:adadelta} Adadelta did not manage to achieve a word similarity of 0.66. It only converged to a similarity of 0.59. It did this in 20 epochs without input shuffling and in 3 with input shuffling, as can be seen in Table \ref{table:results_adadelta}
\begin{table}[h]
\centering
\begin{tabular}{|l|l|l|}
\hline

\end{tabular}
\caption{}
\label{}
\end{table}

\begin{table}[tb]
    \caption{Convergence Time and Quality with Adadelta}
    %\scriptsize
    \begin{tabular}{l r r }%
        \toprule
Adadelta Model & Convergence Time & Word similarity \\ 
        \midrule%
        Without Shuffling & 20 & 0.59 \\ 
With Shuffling & 3 & 0.59 \\
        \midrule%
   \end{tabular}%
   \label{table:results_adadelta}%
\end{table}
